---
title: "2_description"
author: "Aline"
date: '2023-03-10'
output:
  html_document: default
  pdf_document: default
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	fig.align = "center",
	message = FALSE,
	warning = FALSE
)

```

```{r message=FALSE, warning=FALSE, include=FALSE}
# Chargement des packages ----
library(readxl)
library(haven)
library(tidyverse)
library(lubridate)
library(gtsummary)
library(questionr)
library(mice)
library(writexl)
library(gt)
library(expss)
source("~/5. R projects/symbiota_lab/3_programs/1_functions.R", encoding = 'UTF-8', echo=TRUE)
source("~/5. R projects/symbiota_lab/3_programs/0_source_data_reading_cleaning.R", echo=TRUE)
```


# Data evalutation
## Distribution of the maternal and child caracteristics
```{r echo=FALSE, fig.height=2, fig.width=8, message=FALSE, warning=FALSE}
table_descrip_covar <- bdd %>%                        # tableau toutes variables
  filter(!is.na(trajectory))%>%
  select(all_of(vec_covar)) %>% 
  tbl_summary(type = list(GA ~ "continuous", 
                          Smoke_preg ~ "categorical")) %>% 
  bold_labels()
table_descrip_covar_num <- descrip_num(data = bdd, vars = vec_num)   # Tableau détaillé covar num

histogram_descrip_covar <- histogram(data = bdd, vars = vec_covar_num, order_var = vec_covar_num)
boxplot_descrip_covar <-boxplot(data = bdd, vars = vec_covar_num)
densityplot_descrip_covar <-densityplot(data = bdd, vars = vec_covar_num)

table_descrip_covar
histogram_descrip_covar
boxplot_descrip_covar
densityplot_descrip_covar
ggsave(
  densityplot_descrip_covar, 
  device = "pdf", 
  filename= "C:/Users/Aline/OneDrive - etu.univ-grenoble-alpes.fr/Documents/5. R projects/symbiota_lab/4_output/densityplot_descrip_covar.pdf", 
  units = "cm", 
  width = 15, 
  height = 7)
```
```{r echo=FALSE, fig.height=13, fig.width=15, message=FALSE, warning=FALSE}
barplot_descrip_covar <- barplot(data = bdd, vars = vec_covar_cat)
barplot_descrip_covar

ggsave(
  barplot_descrip_covar, 
  device = "pdf", 
  filename= "C:/Users/Aline/OneDrive - etu.univ-grenoble-alpes.fr/Documents/5. R projects/symbiota_lab/4_output/barplot_descrip_covar.pdf", 
  units = "cm", 
  width = 37, 
  height = 20)
```

## Distribution of the gut microbiota enterotypes
```{r echo=FALSE, fig.height=2, fig.width=10, message=FALSE, warning=FALSE}
table_descrip_gut <- bdd %>%                        # tableau toutes variables
  select(all_of(vec_expo)) %>% 
  tbl_summary() %>% 
  bold_labels()
barplot_descrip_gut <- barplot(data = bdd, vars = vec_expo)

table_descrip_gut
barplot_descrip_gut
```

## Distribution of the gut microbiota metabolites 
```{r}
metabolite_vec <- bdd %>% select(starts_with("metabolite")) %>% colnames()
descrip_num(data = bdd, vars = metabolite_vec)

densityplot(data = bdd, vars = metabolite_vec[1:12])
boxplot(data = bdd, vars = metabolite_vec[1:12])

densityplot(data = bdd, vars = metabolite_vec[13:24])
boxplot(data = bdd, vars = metabolite_vec[13:24])

densityplot(data = bdd, vars = metabolite_vec[25:36])
boxplot(data = bdd, vars = metabolite_vec[25:36])

densityplot(data = bdd, vars = metabolite_vec[37:48])
boxplot(data = bdd, vars = metabolite_vec[37:48])

densityplot(data = bdd, vars = metabolite_vec[49:60])
boxplot(data = bdd, vars = metabolite_vec[49:60])

densityplot(data = bdd, vars = metabolite_vec[61:72])
boxplot(data = bdd, vars = metabolite_vec[61:72])

```


## Distribution of Secretory IgA levels 
```{r echo=FALSE, fig.height=3, fig.width=5, message=FALSE, warning=FALSE}
table_descrip_IgA <- bdd %>%                        # tableau toutes variables
  select("sIgA_3m", "sIgA_12mo", "sIgA_3m_cat", "sIgA_12mo_cat") %>% 
  tbl_summary() %>% 
  bold_labels() %>%
  add_n()
table_descrip_IgA_num <- descrip_num(data = bdd, vars = vec_mediator)   # Tableau détaillé covar num

barplot_descrip_IgA <- barplot(data = bdd, vars = c("sIgA_3m_cat", "sIgA_12mo_cat"))

histogram_descrip_IgA <- histogram(data = bdd, vars = vec_mediator, order_var = vec_mediator)
boxplot_descrip_IgA <-boxplot(data = bdd, vars = vec_mediator)
densityplot_descrip_IgA <-densityplot(data = bdd, vars = vec_mediator)

histogram_descrip_IgA_ln <- histogram(data = bdd, vars = vec_mediator_ln, order_var = vec_mediator_ln)
boxplot_descrip_IgA_ln <-boxplot(data = bdd, vars = vec_mediator_ln)
densityplot_descrip_IgA_ln <-densityplot(data = bdd, vars = vec_mediator_ln)



table_descrip_IgA
barplot_descrip_IgA
histogram_descrip_IgA
boxplot_descrip_IgA
densityplot_descrip_IgA

histogram_descrip_IgA_ln
boxplot_descrip_IgA_ln
densityplot_descrip_IgA_ln
```

## Distribution of Bayley scores 
```{r echo=FALSE, fig.height=5, fig.width=8, message=FALSE, warning=FALSE}
table_descrip_neuro <- bdd %>%                        # tableau toutes variables
  select(all_of(vec_outcome)) %>% 
  tbl_summary() %>% 
  bold_labels()
table_descrip_neuro_num <- descrip_num(data = bdd, vars = vec_outcome)   # Tableau détaillé covar num

#barplot_descrip_neuro <- barplot(data = bdd, vars = )
histogram_descrip_neuro <- histogram(data = bdd, vars = vec_outcome, order_var = vec_outcome)
boxplot_descrip_neuro <-boxplot(data = bdd, vars = vec_outcome)
densityplot_descrip_neuro <-densityplot(data = bdd, vars = vec_outcome)

table_descrip_neuro_num
#barplot_descrip_neuro
histogram_descrip_neuro
boxplot_descrip_neuro
densityplot_descrip_neuro
```

## Correlations between the continuous variables 
```{r echo=FALSE, fig.height=15, fig.width=15, message=FALSE, warning=FALSE}
cormat <- bdd %>% select(all_of(vec_covar_num), all_of(vec_mediator), all_of(vec_outcome)) 
cormat <- round(cor(cormat, 
                      use = "pairwise.complete.obs", 
                      method = "spearman"), 2)
cormat
```

## Missing data and sample size evaluation 
```{r echo=FALSE, message=FALSE, warning=FALSE}
sample_size_1 <- bdd %>% 
  select(all_of(vec_expo), all_of(vec_mediator)) %>% 
  md.pattern(plot = FALSE) 

sample_size_2 <- bdd %>% 
  filter(!is.na(trajectory)) %>%
  select(all_of(vec_mediator), all_of(vec_outcome)) %>% 
  md.pattern(plot = FALSE)  

sample_size_3 <- bdd %>% 
  select(all_of(vec_expo), all_of(vec_outcome)) %>% 
  md.pattern(plot = FALSE)

sample_size_4 <- bdd %>% 
  select(all_of(vec_expo), all_of(vec_mediator), all_of(vec_outcome)) %>% 
  md.pattern(plot = FALSE)

sample_size_1
sample_size_2
sample_size_3
sample_size_4


```

## Outliers evaluation
```{r echo=FALSE, message=FALSE, warning=FALSE}
outliers(bdd, sIgA_3m_ln)
outliers(bdd, sIgA_12mo_ln)
```

# Data description
## Maternal and child characteristics depending on gut microbiota enterotypes 
```{r echo=FALSE, message=FALSE, warning=FALSE}

t1 <- bdd %>%
  filter(!is.na(Cluster_3M)) %>%
  select(all_of(vec_covar), Cluster_3M) %>%
  tbl_summary(by = Cluster_3M, 
              type = list(GA ~ "continuous", 
                          Smoke_preg ~ "categorical")) %>%
  add_overall() %>%
  add_p() %>%
  bold_labels() %>%
  bold_p()

t2 <- bdd %>%
  filter(!is.na(Cluster_12M)) %>%
  select(all_of(vec_covar), Cluster_12M) %>%
  tbl_summary(by = Cluster_12M, 
              type = list(GA ~ "continuous",
                          Smoke_preg ~ "categorical")) %>%
  add_p() %>%
  bold_labels()%>%
  bold_p()

t3 <- bdd %>%
  filter(!is.na(trajectory)) %>%
  select(all_of(vec_covar), trajectory) %>%
  tbl_summary(by = trajectory, 
               type = list(GA ~ "continuous",
                          Smoke_preg ~ "categorical")) %>%
  add_p() %>%
  bold_labels()%>%
  bold_p()

table_covar_gut <- tbl_merge(
  tbls = list(t1, t2, t3), 
  tab_spanner = c("Clusters at 3 months", "Clusters at 12 months", "Trajectory"))

table_covar_gut 
```

## Maternal and child characteristics distribution and gut microbiota enterotypes depending on IgA levels
```{r echo=FALSE, message=FALSE, warning=FALSE}
t4 <- bdd %>%
  filter(!is.na(trajectory)) %>%
  select(all_of(vec_covar), all_of(vec_expo), sIgA_3m_cat) %>%
  tbl_summary(by = sIgA_3m_cat,
                 type = list(GA ~ "continuous",
                             Smoke_preg ~ "categorical")) %>%
  add_overall() %>%
  add_p() %>%
  bold_labels()%>%
  bold_p()

t5 <- bdd %>%
  filter(!is.na(trajectory)) %>%
  select(all_of(vec_covar), all_of(vec_expo), sIgA_12mo_cat) %>%
  tbl_summary(by = sIgA_12mo_cat,
                 type = list(GA ~ "continuous",
                             Smoke_preg ~ "categorical")) %>%
  add_p() %>%
  bold_labels()%>%
  bold_p()

table_covar_gut_IgA <- tbl_merge(
  tbls = list(t4, t5), 
  tab_spanner = c("IgA at 3 months", "IgA at 12 months"))

table_covar_gut_IgA
```

## Maternal and child characteristics distribution, gut microbiota enterotypes and serun IgA levels depending on Bayley score
```{r eval=FALSE, message=FALSE, warning=FALSE, include=FALSE}
t6 <- bdd %>%
  filter(!is.na(trajectory)) %>%
  select(all_of(vec_covar), all_of(vec_expo), all_of(vec_mediator), sIgA_3m_cat, sIgA_12mo_cat) %>%
  tbl_summary(by = xxx,
                 type = list(GA ~ "continuous",
                             Smoke_preg ~ "categorical")) %>%
  add_overall() %>%
  add_p() %>%
  bold_labels()%>%
  bold_p()

t7 <- bdd %>%
  filter(!is.na(trajectory)) %>%
  select(all_of(vec_covar), all_of(vec_expo), all_of(vec_mediator), sIgA_3m_cat, sIgA_12mo_cat) %>%
  tbl_summary(by = xxx,
                 type = list(GA ~ "continuous",
                             Smoke_preg ~ "categorical")) %>%
  add_p() %>%
  bold_labels()%>%
  bold_p()

table_covar_gut_IgA_neuro <- tbl_merge(
  tbls = list(t6, t7), 
  tab_spanner = c("Bayley score at 1 year", "Bayley score at 2 years"))

table_covar_gut_IgA_neuro
```
